GSS Education Analysis (Working Title)

### 2023-03-16 outputs/paper/paper.qmd
update references and future research section

By looking at @fig-4 we can see that most respondents are "moderately satisfied" or higher with their current employment. Although each has

@@

According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement**(citation).** These are the fundamentals in terms of how Americans generally define their well-being in society. However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer. But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.

@@

The second largest group of participants who had completed the survey had completed a bachelor's degree. In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem. According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups. The majority for both groups claimed to be average or above average. There was still a significant number of individuals who had chosen below average, even for the group with the highest level of education.

A similar notion exists when comparing an individuals level of education with their job satisfaction. According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\". This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction. According to @fig-3, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.

@@

# Further reseach  {#sec-fur-reseach}

@@

# Appendix

@@

Supplementary survey is available: [here](https://forms.gle/vUCXy927cDnpx5UL9)

>>>>

By looking at @fig-4 we can see that those who rank themselves as "above average" or higher in comparison to other US families, are also more likely to describe themselves as "upper class" than those who rank themselves lower. This indicates that respondents are likely self aware of there financial status as it relates to social class. This is emphasized in @fig-4, as the opposite is also true with respondents who rate themselves as "below average" or lower, being more likely to describe themselves as "lower class." Interestingly, respondents who rank themselves as average in comparison to other US families tended to rank themselves as "working class" or "middle class" with only 12 respondents claiming to be of "lower class" and 1 respondent claiming to be of "upper class" from this grouping.

@@

According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement [@citerankhirschl]**.** These are the fundamentals in terms of how Americans generally define their well-being in society. However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer. But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.

@@

The second largest group of participants who had completed the survey had completed a bachelor's degree. In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem. According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor's degree, the reported financial ranking against other families was proportionately very similar for both groups. The majority for both groups claimed to be average or above average. There was still a significant number of individuals who had chosen below average, even for the group with the highest level of education.

A similar notion exists when comparing an individuals level of education with their job satisfaction. According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor's or graduate degree still consists of those that chose "Moderately Satisfied", "A Little Dissatisfied", and "Very Dissatisfied". This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction. According to @fig-3, the two highest levels of education still make up a significant portion of the "More or Less Satisfied" and the "Not Satisfied at All'' groups.

@@

# Future Research {#sec-fur-reseach}

More research into this topic is important as it helps us gain a more substantial understanding of American ideals and how certain indicators may influence the rate at which individuals are achieving them, or not achieving them. Further research into this topic should explore more specific questions about attitudes towards work, type of work, income, and comparing respondent situations to close acquaintances to better understand American perspectives. We have provided a supplementary survey in @sec-appendix that would further build on the US GSS data in relation to our topic. Additionally, future research should be conducted over a period of time using the same survey and methodology to better obtain information that is verifiable and encompasses a larger population of the United States.

@@

# Appendix {#sec-appendix}

@@

The supplementary survey is available: [here](https://forms.gle/vUCXy927cDnpx5UL9)

```{r, out.width = "500px"}
#| echo = FALSE

#### Import .png Files of Supplementary Survey ####

knitr::include_graphics("./supplementary_survey/suppl_surv_01.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_2.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_3.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_4.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_5.png")
knitr::include_graphics("./supplementary_survey/suppl_surv_6.png")
